Individual Differences Across Visual Search Tasks

### 2017-01-20 writeup/manuscript.tex
added figures for feature design
starting to look at pilot data
but missing fix asc processing file

\documentclass[a4paper, oneside, 11pt, onecolumn]{article}
\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage[round, comma, sort&compress, longnamesfirst]{natbib} 
% \usepackage[left=2cm,top=3cm,right=1.5cm,bottom=2cm,bindingoffset=0.5cm]{geometry}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage[title,titletoc,toc]{appendix}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyfoot[L]{\textit{running footer}}
 \fancyhead[L]{\textit{running title}}
\renewcommand{\headrulewidth}{0.8pt}
\renewcommand{\footrulewidth}{0.8pt}
\setlength\headheight{14pt}
\fancyfoot[RO] {\thepage}
\usepackage{authblk}
%%%%%%%%%%%%

@@

@@

>>>>

\documentclass[a4paper, oneside, 11pt, onecolumn]{article}
\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[round, comma, sort&compress, longnamesfirst]{natbib} 
% \usepackage[left=2cm,top=3cm,right=1.5cm,bottom=2cm,bindingoffset=0.5cm]{geometry}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage[title,titletoc,toc]{appendix}
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyfoot[L]{\textit{running footer}}
 \fancyhead[L]{\textit{running title}}
\renewcommand{\headrulewidth}{0.8pt}
\renewcommand{\footrulewidth}{0.8pt}
\setlength\headheight{14pt}
\fancyfoot[RO] {\thepage}
\usepackage{authblk}
%%%%%%%%%%%%

@@

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=6cm]{../NowakowskaClarkeHunt2017/scripts/r_by_nfix.pdf}}
\subfigure[][]{\includegraphics[width=6cm]{../NowakowskaClarkeHunt2017/scripts/best_r_scatter.pdf}}
\caption{Selecting the best $n$.}
\label{fig:nowakowskaBestN}
\end{figure}

@@

\subsubsection{}

\subsection{Exploratory Analysis}

We will carry out additional analysis, above and beyond what has been documented above, but the exact nature of this will be contingent on the nature of the results. Something like PCA may be interesting.
